What paradigms can webcam eye-tracking be used for? Attempted replications of five ``classic'' cognitive science experiments

### 2025-03-20 group-c/E3-analysis-replication.Rmd

We calculated the proportion of gaze samples in the ROI of the unfamiliar image out of all the gaze samples that were in either ROI. Of the `r looking.score.data %>% nrow()` trials in the experiment, `r looking.score.data %>% filter(is.nan(looking.score)) %>% nrow()` had no fixations in either ROI and so were excluded from this analysis.

@@

To see whether preferentially looking an the unfamiliar object on day 1 was correlated with confidence and response time for correct responses on Day 2, we computed the correlation coefficient between Day 1 proportion looks to novel and Day 2 confidence/RT for each participant. Following the original analysis, we transformed these values using the Fisher p-to-z transformation. Using one-sample t-tests, failed to replicate the a significant difference from 0 for the correlation between proportion looks to the novel object and confidence ratings, t(`r looking.confidence.correlation.t.test$parameter`) = `r looking.confidence.correlation.t.test$statistic`, p = `r looking.confidence.correlation.t.test$p.value` (excluding the subjects who gave the same confidence judgment for all images), nor for the correlation with RT, t(`r  looking.rt.correlation.t.test$parameter`) = `r looking.rt.correlation.t.test$statistic`, p = `r looking.rt.correlation.t.test$p.value`.

>>>>

We calculated the proportion of gaze samples in the ROI of the unfamiliar image out of all the gaze samples that were in either ROI. Of the `r looking.score.data %>% nrow()` total trials in the experiment across all subjects, `r looking.score.data %>% filter(is.nan(looking.score)) %>% nrow()` had no fixations in either ROI and so were excluded from this analysis.

@@

To see whether preferentially looking an the unfamiliar object on day 1 was correlated with confidence and response time for correct responses on Day 2, we computed the correlation coefficient between Day 1 proportion looks to novel and Day 2 confidence/RT for each participant. Following the original analysis, we transformed these values using the Fisher p-to-z transformation. Using one-sample t-tests, we failed to replicate the a significant difference from 0 for the correlation between proportion looks to the novel object and confidence ratings, t(`r looking.confidence.correlation.t.test$parameter`) = `r looking.confidence.correlation.t.test$statistic`, p = `r looking.confidence.correlation.t.test$p.value` (excluding the subjects who gave the same confidence judgment for all images), nor for the correlation with RT, t(`r  looking.rt.correlation.t.test$parameter`) = `r looking.rt.correlation.t.test$statistic`, p = `r looking.rt.correlation.t.test$p.value`.

### 2025-03-20 manuscript.Rmd

This plug-in (and potentially other webcam-based eye-tracking options) opens the door to including a broader, more diverse sample of participants in cognitive science research. In contrast to the typical in-lab eye-tracking sample, which consists primarily of young university students from WEIRD countries, webcam eye-tracking can reach much larger numbers of participants of all ages, across the globe, as the only prerequisite is access to a computer with a webcam (a standard feature on most modern laptops). Characterizing the diversity of populations that webcam eye-tracking studies can reach is an important avenue for future work.

@@

4. **Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.** Results from an in-lab study with an eyetracker (Panel A; @james2023language) are contrasted with the current results (Panel B). The vertical line marks the mean noun onset time across trials and conditions.

>>>>

This plug-in (and potentially other webcam-based eye-tracking options) opens the door to including a broader, more diverse sample of participants in cognitive science research. In contrast to the typical in-lab eye-tracking sample, which consists primarily of young university students from WEIRD countries [@henrich2010weirdest; @linxen2021weird; @de2023psychology; @rad2018toward], webcam eye-tracking can reach a much more diverse population, as the only prerequisite is access to a computer with a webcam (a standard feature on most modern laptops and tablets). While webcam eyetracking cannot by itself eliminate all demographic biases, some of which are in any case baked in by history [@henrich2020weirdest], it can help to reduce them, at least for studies amenable to the paradigm.

@@

4. **Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time.** Results from an in-lab study with an eyetracker (Panel A; James et al. 2023) are contrasted with the current results (Panel B). The vertical line marks the mean noun onset time across trials and conditions.
